### 2012-05-10 Rctl/inst/doc/manual.Rnw
[Rctl] More manual updates

\textbf{\sffamily Abstract}: Tutorial for the Correlated Trait Loci (CTL) mapping to reconstruct
genetic regulatory networks using the R package 'ctl' and the mapctl commandline tool. This 
tutorial is targetted at people with a basic understanding of genetics and would like to analyse
there inbred cross or natural population. Main focus will be explaining the functionality of the 
software, and a how-to on loading datasets via Excel, tab delimited files (.csv) and R/qtl. In 
the methodology and background only a short introduction in CTL mapping theory is given.

>>>>

\textbf{\sffamily Abstract}: Tutorial for the Correlated Trait Loci (CTL) mapping package to 
reconstruct genetic regulatory networks using the R package 'ctl' and the mapctl commandline 
tool. 
This tutorial is targetted at people with a basic understanding of genetics and would like to 
analyse there inbred cross or natural population. Main focus will be explaining the functionality 
of the software, and a how-to on loading datasets via Excel, tab delimited files (.csv) and 
R/qtl. In the methodology and background only a short introduction in CTL mapping theory is 
given.
